\documentclass{article}
\usepackage{enumitem}

\begin{document}

\section*{Elena Cavalli}
elena.cavalli@equine.com | +39 345-678-9012 \\
LinkedIn: linkedin.com/in/elena-cavalli

\section*{EDUCATION}

\textbf{Master of Science in Equine Studies} \\
September 2021 - December 2023 \\
University of Pisa (Italy) \\
Final grade: 110/110 \\
Thesis: "Advanced Techniques in Equine Behavior Analysis and Training"

\textbf{Erasmus – Master of Science in Equine Sciences} \\
October 2021 - February 2022 \\
University of Edinburgh (United Kingdom)

\textbf{Bachelor’s degree in Animal Science} \\
September 2018 - April 2021 \\
University of Pisa (Italy)

\section*{SKILLS}

\textbf{Equine Training Techniques:} Dressage | Jumping | Natural Horsemanship | Equine Therapy

\textbf{Technologies and Tools:} Equine Management Software | GPS Tracking Systems | Veterinary Diagnostic Tools | Horse Breeding Databases

\textbf{Languages:} Italian - mother tongue | English - proficient

\section*{EXPERIENCE}

\textbf{Equine Excellence Center – Pisa (Italy)} \\
January 2024 - Present \\
Equine Specialist and Trainer \\
\begin{itemize}[leftmargin=*]
    \item Developed and implemented advanced training programs for competitive dressage and jumping horses, achieving a 20\% improvement in performance metrics.
    \item Conducted workshops on natural horsemanship techniques, improving horse-rider communication and reducing training-related stress in horses.
    \item Collaborated with veterinarians to integrate therapeutic exercises into training regimens, enhancing recovery rates for injured horses.
\end{itemize}

\section*{NOTABLE PROJECTS}

\textbf{Equine Behavior Analysis Tool} \\
September 2024 - Present \\
Equine Excellence Center (Italy) \\
\begin{itemize}[leftmargin=*]
    \item Developed a software tool to analyze and predict equine behavior patterns using machine learning algorithms.
    \item Integrated GPS tracking and biometric data to provide real-time insights into horse behavior and training effectiveness.
    \item Collaborated with researchers to publish findings in leading equine science journals.
\end{itemize}

\textbf{Equine-Assisted Learning Program} \\
April 2024 - Present \\
Horse Haven (Italy) \\
\begin{itemize}[leftmargin=*]
    \item Designed an educational program for children and adolescents using horses to teach life skills and emotional regulation.
    \item Implemented the program in collaboration with local schools, reaching over 200 students in the first year.
    \item Evaluated program effectiveness through pre- and post-program assessments, showing significant improvements in participants' social and emotional skills.
\end{itemize}

\end{document}